Self Regulation Ontology Retest Data Report

### 2017-03-21 SRO_Report.Rmd
working on new report

---
title: 'Self Regulation Ontology Retest Data Report'
output:
html_document:
toc: yes
toc_float: yes
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
library(rmarkdown)
library(psych)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
```

@@

>>>>

---
title: 'Self Regulation Ontology Retest Data Report'
output:
github_document:
toc: yes
toc_float: yes
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
library(rmarkdown)
library(psych)
library(stringr)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
```

@@

tmp %>%
  spread(time, score) %>%
  # mutate(dv_wrap = str_wrap(dv, width = 30)) %>%
  ggplot(aes(`1`, `2`))+
  geom_point()+
  theme_bw()+
  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())
